### 2019-11-25 Mathematical Statatistics/ms_ch_03.rmd
ms, ch3 exercises

#### Section

### Subsection

>>>>

#### Chapter 3 Exercises

### 3.1

Suppose you conduct an experiment and inject a drug into three mice.

Their times for running a maze are 8, 10, 15 s; the times for two control mice are 5 and 9 s.

a.) Compute the difference in mean times between the treatment group and the control group.

```{r, echo = T}
```

b.) Write out all the possible permutations of these times to the two groups and calculate the diffence in means.

```{r, echo = T}
```
c.) What proportion of the differences are as large or larger than the observed differences in mean times?

```{r, echo = T}
```

d.) For each permutation, calculate the mean of the treatment group only.

What proportion of these means are as large or larger than the observed mean of the treatment group?

```{r, echo = T}
```

### 3.2
